---
title: 'Supplementary file 1: annotated R-script for lme-AIC/logLikelihood analysis
  for journal-level metrics'
author: "Jeff C. Clements, Rémi M. Daigle, Halley E. Froehlich"
date: "Feb 7, 2018"
output: pdf_document
---

If necessary, install the package `nlme`
```{r install, eval=FALSE}
install.packages("nlme")
```

Load the package:
```{r load}
library(nlme)
```

Upload data file for time since inception, number of papers per year
```{r}
journals <- read.csv("Table S1_journal_level.csv",stringsAsFactors = FALSE)
names(journals)
```

Natural log transform Years running, OA APC, and Avg papers per year
```{r}
journals$lnYearsRunning <- log(journals$Years.running)
journals$lnOA_APC <- log(journals$OA.APC..USD.)
journals$lnAvgPapersPerYear <- log(journals$Avg.papers.per.year)
```


lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on time since inception.
```{r}
j1.lme<-lme(lnYearsRunning~ Non.Indexed,random=~1|Journal,data=journals)
anova(j1.lme)
```

```{r}
j1.gls<-gls(lnYearsRunning~ Non.Indexed,data=journals)
anova(j1.lme,j1.gls)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on number of papers per year.

```{r}
j2.lme<-lme(lnAvgPapersPerYear~ Non.Indexed,random=~1|Journal,data=journals)
anova(j2.lme)
```

```{r}
j2.gls<-gls(lnAvgPapersPerYear~ Non.Indexed,data=journals)
anova(j2.lme,j2.gls)
```

lme and AIC/LogLikelihood for effect of journal [random] and journal type [fixed] on open access APC
```{r}
j3.lme<-lme(lnOA_APC~Non.Indexed,random=~1|Journal,data=journals,na.action = "na.omit")
anova(j3.lme)
```

```{r}
j3.gls<-gls(lnOA_APC~Non.Indexed,data=journals,na.action = "na.omit")
anova(j3.lme,j3.gls)
```

