---
title: 'Supplementary file 3: annotated R-script for lme-AIC/logLikelihood analysis for demographic article-level metrics'
author: "Jeff C. Clements, Rémi M. Daigle, Halley E. Froehlich"
date: "Feb 7, 2018"
output: pdf_document
---

If necessary, install the package `nlme`
```{r install, eval=FALSE}
install.packages("nlme")
```

Load the package:
```{r load}
library(nlme)
```

Upload data file for demographic proportions
```{r}
demographic <- read.csv("TableS3_proportions.csv",stringsAsFactors = FALSE)
names(demographic)
```

Arcsine transform the proportion data
```{r}
demographic$arcProp.developing.corr.authors <- asin(demographic$X.b..Prop.developing.corr.authors)
demographic$arcProp.developing.other.authors <- asin(demographic$X.c..Prop.developing.other.authors)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on proportion of corresponding authors from developing countries
```{r}
demo.lme<-lme(arcProp.developing.corr.authors~Non.Indexed,random=~1|Journal,data=demographic)
anova(demo.lme)
```
```{r}
demo.gls<-gls(arcProp.developing.corr.authors~Non.Indexed,data=demographic)
anova(demo.lme,demo.gls)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on proportion of additional authors from developing countries
```{r}
demo2.lme<-lme(arcProp.developing.other.authors~Non.Indexed,random=~1|Journal,data=demographic)
anova(demo2.lme)
```

```{r}
demo3.gls<-gls(arcProp.developing.other.authors~Non.Indexed,data=demographic)
anova(demo2.lme,demo3.gls)
```
