---
title: 'Supplementary file 2: annotated R-script for lme-AIC/logLikelihood analysis for non-demographic article-level metrics'
author: "Jeff C. Clements, Rémi M. Daigle, Halley E. Froehlich"
date: "July 25, 2017"
output: pdf_document
---

If necessary, install the package `nlme`
```{r install, eval=FALSE}
install.packages("nlme")
```

Load the package:
```{r load}
library(nlme)
```

Upload data file for time since inception, number of papers per year
```{r}
nondemographic <- read.csv("Table S2_Pred pubs.csv",stringsAsFactors = FALSE)
names(nondemographic)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on the number of authors per article.
```{r}
nondemo1.lme<-lme(X..authors~Predatory.,random=~1|Journal,data=nondemographic)
anova(nondemo1.lme)

```
```{r}
nondemo1.gls<-gls(X..authors~Predatory.,data=nondemographic)
anova(nondemo1.lme,nondemo1.gls)

```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on the length of articles
```{r}
nondemo2.lme<-lme(Article.length....pgs.~Predatory.,random=~1|Journal,data=nondemographic)
anova(nondemo2.lme)
```

```{r}
nondemo2.gls<-gls(Article.length....pgs.~Predatory.,data=nondemographic)
anova(nondemo2.lme,nondemo2.gls)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on the number of references per article.
```{r}
nondemo3.lme<-lme(X..of.references~Predatory.,random=~1|Journal,data=nondemographic)
anova(nondemo3.lme)
```

```{r}
nondemo3.gls<-gls(X..of.references~Predatory.,data=nondemographic)
anova(nondemo3.lme,nondemo3.gls)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on the number of figures and tables per article.
```{r}
nondemo4.lme<-lme(X..figs...tables~Predatory.,random=~1|Journal,data=nondemographic,na.action='na.omit')
anova(nondemo4.lme)
```

```{r}
nondemo4.gls<-gls(X..figs...tables~Predatory.,data=nondemographic,na.action='na.omit')
anova(nondemo4.lme,nondemo4.gls)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on the time from acceptance to publication

```{r}
nondemo5.lme<-lme(Time.sub.accept..days.~Predatory.,random=~1|Journal,data=nondemographic,na.action='na.omit')
anova(nondemo5.lme)
```


```{r}
nondemo5.gls<-gls(Time.sub.accept..days.~Predatory.,data=nondemographic,na.action='na.omit')
anova(nondemo5.lme,nondemo5.gls)
```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on the time from submission to acceptance
```{r}
nondemo6.lme<-lme(Time.accept.pub..days.~Predatory.,random=~1|Journal,data=nondemographic,na.action='na.omit')
anova(nondemo6.lme)
```

```{r}
nondemo6.gls<-gls(Time.accept.pub..days.~Predatory.,data=nondemographic,na.action='na.omit')
anova(nondemo6.lme,nondemo6.gls)
```
Model df      AIC      BIC    logLik   Test  L.Ratio p-value
nondemo6.lme     1  4 1726.690 1739.418 -859.3452                        
nondemo6.gls     2  3 1809.035 1818.581 -901.5176 1 vs 2 84.34492  <.0001


Upload data file for demographic proportions
```{r}
demographic <- read.csv("TableS3_proportions.csv",stringsAsFactors = FALSE)
names(demographic)
```

Arcsine transform the proportion data
```{r}
demographic$arcProp.statistics.reported <- asin(demographic$X.d..Prop.statistics.reported)
demographic$arcProp.stats.adequate <- asin(demographic$X.e..Prop.stats.adequate)

```

lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on proportion of article reporting general statistical analyses
```{r}
nondemo7.lme<-lme(arcProp.statistics.reported~Predatory.,random=~1|Journal,data=demographic)
anova(nondemo7.lme)
```
```{r}
nondemo7.gls<-gls(arcProp.statistics.reported~Predatory.,data=demographic)
anova(nondemo7.lme,nondemo7.gls)
```


lme and AIC/logLikelihood for effect of journal [random] and journal type [fixed] on proportion of article reporting details of statistical analyses
```{r}
nondemo8.lme<-lme(arcProp.stats.adequate~Predatory.,random=~1|Journal,data=demographic)
anova(nondemo8.lme)
```

```{r}
nondemo8.gls<-gls(arcProp.stats.adequate~Predatory.,data=demographic)
anova(nondemo8.lme, nondemo8.gls)
```

